Community-Conditioned Language Models

### 2020-11-11 paper/paper.tex
revise hypotheses

- What are linguistic communities
  - Linguistic complexity
- Conditioned language models

@@

\begin{hypotheses}
\item Different communities have different levels of linguistic
  complexity
\item Different language models are able to recognize such differences
\item The level at which the community embedding is taken into account
  in the language model influences this.
\item Community embedding are correlated with extra-linguistic
  properties of the community.
\item Community stability is correlated with language complexity
\end{hypotheses}

>>>>

- What are linguistic communities
  - Linguistic complexity
- Community Conditioned language models
- Latent Community Classifier

@@

\begin{hypotheses}
\item Different communities have different levels of linguistic
  complexity

\item LCC works: the communty-specific linguistic features are recognized by CCLM.
\item The layer at which the community embedding is taken into account
  in CCLM influences its perplexity.
\item The layer at which the community embedding is taken into account
  influences the LCC.
\item Correlation between community language complexity and recognisability. (False)
\item Community embedding are correlated with coocurrence of users
  between communities.
% \item Community stability is correlated with language complexity
\end{hypotheses}
